An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-13 indicators/paper/paper.tex
Title tweak?
Bunch of keywords
Add repo URL, small tweaks

\title{An Open-Source Repository of Real-Time COVID-19 Indicators}

@@

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{open data $|$ COVID-19 $|$ Keyword 3 $|$ ...}

@@

For many purposes it is sufficient to use the most recently issued observation
for any time value, and thus the COVIDcast API reports the most recent issue by
default. However, for some applications it is crucial to know what was known
\textit{as of} a specific date. For example, an epidemic forecasting model will
be called upon to make its forecasts based on preliminary data about recent
trends, and so when it is trained using historical data, it should be trained
using the initial versions of that data, not updates that would have been
received later. Furthermore, these revision records allow models to be modified
to account for noise and bias in early data versions, or to exclude data that is
too new to be considered stable, and to ``rewind'' time and simulate how these
revised models would have performed using only the versions of data available
\textit{as of} those times.

Research on data revisions in the context of influenza-like illness has shown
that backfill can significantly alter forecast performance \cite{Brooks:2018,
  Reich:2019}, and that training to use preliminary data can reduce this
influence \cite{Brooks:2018, Brooks:2020}. This is also investigated in our
companion paper on forecasting, where we observe that training and validating
models on finalized data yields overly optimistic estimates of true test-time
performance.

@@

In what follows, we present illustrative examples of the usefulness of some of
the novel signals available in the API. These examples demonstrate that such
indicators are meaningfully related to COVID activity, that they provide
alternate views on pandemic activity that are not subject to the same reporting
glitches and delays as traditional public health surveillance streams, and that
they provide information about public behavior and attitudes that are not
available from any other source. Code to reproduce all examples (which uses the
\texttt{covidcast} R package and fetches data directly from the API) can be
found at \url{TODO}.

>>>>

\title{An Open Repository of Real-Time COVID-19 Indicators}

@@

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{open data $|$ COVID-19 $|$ digital surveillance $|$ medical insurance
  claims $|$ internet surveys $|$ search trends $|$ mobility patterns}

@@

For many purposes it is sufficient to use the most recently issued observation
at any a given time value, and the COVIDcast API returns the most recent issue
as its default. However, for some applications it is crucial to know what was
known \textit{as of} a specific date. For example, an epidemic forecasting model
will be called upon to make its forecasts based on preliminary data about recent
trends, so when it is trained using historical data, it should be trained using
the initial versions of that data, not updates that would have been received
later. Moreover, these revision records allow models to be modified to account
for noise and bias in early data versions, or to exclude data that is too new to
be considered stable, and to ``rewind'' time and simulate how these revised
models would have performed using only the versions of data available \textit{as
of} those times.

Research on data revisions in the context of influenza-like illness has shown
that backfill can significantly alter forecast performance \cite{Brooks:2018,
  Reich:2019}, and that careful training on preliminary data can reduce this
influence \cite{Brooks:2020}. We also investigate this in our companion paper on
forecasting, where we observe that training and validating models on finalized 
data yields overly optimistic estimates of true test-time performance.

@@

In what follows, we present illustrative examples of the usefulness of some of
the novel signals available in the API. These examples demonstrate that such
indicators are meaningfully related to COVID activity, that they provide
alternate views on pandemic activity that are not subject to the same reporting
glitches and delays as traditional public health surveillance streams, and that
they provide information about public behavior and attitudes that are not
available from any other source. Code to reproduce all examples (which uses the
\texttt{covidcast} R package and fetches data directly from the API) can be
found at
\url{https://www.github.com/cmu-delphi/covidcast-pnas/indicators/code/}.
